---
title: "Page Ranking Over Time"
author: "Larry Lathrop"
date: "2/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Google Search Console

I had this crazy thought I thought I would share. I was wondering what is the page ranking over time by page in Google Search Console.  I would like to build something that gives me insight on how webpage performs over time. This is something you really do not get with the Google Search Console.

The packages I will need are as follows:
```{r libraries}
library(googleAuthR)
library(searchConsoleR)
library(tidyverse)

```


##After installing the 


```{r Checking my site lis}
#Cheking what sites I have

list_websites()

#checked to see if I can see the site map for the owllytics site.
list_sitemaps("https://www.owllytics.com")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
